Centralizers of higher enveloping algebras and their large $N$ limits

### 2019-05-19 frame.tex

\begin{dfn}
Let $A$ be a dg algebra over $k$, and let $\cA = A \otimes \Omega^*_c$ denote the associated cosheaf of dg algebras on~$\RR^n$.
Let $\cC_A$ denote the precosheaf $\Cyc_*(\cA)[1]$ of cochain complexes on $\RR^n$,
which assigns to each open set $U$, the 1-shifted cyclic chains on $\cA(U)$.
\end{dfn}
\greg{Here we shall either recall our model for cyclic chains, or first define the $\infty$-categorical universal statement and then precise a nice model. By the universal model, I mean define cyclic as the homotopy $S^1$-fixed point for the action on Hochschild chains. This will make the construction more transparent ?}
\mahmoud{cyclic is the homotopy quotient and negative cyclic the homotopy fixed points}
Note that for two algebras $B$ and $B'$,
\[
\Cyc_*(B) \oplus \Cyc_*(B') \simeq \Cyc_*(B \times B') .
\] 
The corresponding statement for ordinary Hochschild homology is induced by the projections $B \leftarrow B \times B' \to B'$, and any map of algebras that induces a quasi-isomorphism on Hochschild homology induces one on cyclic homology as well.
(See, for instance, \S2.2.12 of \cite{LodayCyclic}.)
Hence, for any finite collection of disjoint opens $U_1$, \dots, $U_k$, 
we have
\[
\cC_A(U_1 \sqcup \cdots \sqcup U_k) \simeq \cC_A(U_1) \oplus \cdots \oplus \cC_A(U_k).
\]
Moreover, for any nested sequence of inclusions $V_1 \subset V_2 \subset \cdots$ with $V = \bigcup_i V_i$,
there is a quasi-isomorphism
\[
{\rm hocolim}(\cC_A(V_1) \to \cC_A(V_2) \to \cdots) \simeq \cC_A(V).
\]
(See E.2.1.1 of \cite{LodayCyclic}.)
In this sense $\cC_A$ behaves like a cosheaf, up to quasi-isomorphism. 
This property underlies the following claim.

@@

\section{\owen{A stub about a twisted version of LQT}}

\owen{Brian and I will later insert an expansion of the following.}

Let $\chi \in \Cyc^m(A)$ is a cyclic cocycle of degree $m$. 
Then $\chi$ determines a central extension $\cC(A)_\chi$ of $\Cyc_*(A)[1]$ as an abelian Lie algebra (cf. Heisenberg Lie algebras),
but $\chi$ also maps to Lie algebra cochains $\clies(\gl_N(A))$ for every $N$ via the LQT map,
and hence determines a central extension $\gl_N(A)_\chi$ of $\gl_N(A)$ as well.
There is thus a $\chi$-twisted version of the LQT map
\[
\lqt_\chi: \Sym(\cC(A)_\chi) \to \cliels(\gl_N(A)_\chi)
\]
which is a quasi-isomorphism in the large $N$ limit.

This induces $\chi$-twisted versions of all our enveloping $E_n$ algebra theorems (in large $N$ limit).

%We briefly remark on a natural modification of the prefactorization algebra $\Sym(\cC_A)$. 
%For simplicity, suppose $A$ is an ordinary (non dg) algebra, and let $\chi \in \Cyc^m(A)$ be a cyclic {\em cocycle} of degree $m$.
%Consider for each open $U \subset \RR^n$ the cochain complex
%\[
%\Tilde{\cC}_{A,\chi} (U) = \left(\Cyc_*(A \tensor \Omega^*_c(U))[1] \oplus \CC \cdot K , \d_{\rm Cyc} + K \cdot \chi \right) 
%\]
%where $K$ is a formal parameter of degree $-m+n+1$.
%Also, $\d_{\rm Cyc}$ is the cyclic differential and $\chi$ is defined on $m$-chains by the pairing between cyclic chains and cochains, together with integration along $U$:
%\[
%\chi ((a_1 \otimes \alpha_1) \tensor \cdots \tensor (a_m \otimes \alpha_m)) = \int_U \<\chi, a_1 \tensor \cdots \tensor a_m\> \alpha_1 \wedge \cdots \wedge \alpha_m.
%\]
%The differential is extended to the entire cochain complex by the graded Leibniz rule. 
%By similar arguments as above, the assignment $U \subset \Tilde{\cC}_{A, \chi}$ is a precosheaf of cochain complexes and $\Sym\left(\Tilde{\cC}_{A,\chi}\right)$ is a prefactorization algebra. 
%As a precosheaf of graded vectors spaces one has $\Tilde{\cC}_{A, \chi} = \cC_A \oplus \ul{\CC}[m-n-1]$, where $\ul{\CC}$ is the constant precosheaf, so that we may think of $\Sym\left(\Tilde{\cC}_{A,\chi}\right)$ as a twisted version of $\Sym(\cC_A)$. 
%These types of twisted \brian{what to say? check my degrees!}
%

>>>>

\begin{dfn}\label{dfn: CA}
Let $A$ be a dg algebra over $k$, and let $\cA = A \otimes \Omega^*_c$ denote the associated cosheaf of dg algebras on~$\RR^n$.
Let $\cC_A$ denote the precosheaf $\Cyc_*(\cA)[1]$ of cochain complexes on $\RR^n$,
which assigns to each open set $U$, the 1-shifted cyclic chains on $\cA(U)$.
\end{dfn}
\greg{Here we shall either recall our model for cyclic chains, or first define the $\infty$-categorical universal statement and then precise a nice model. By the universal model, I mean define cyclic as the homotopy $S^1$-fixed point for the action on Hochschild chains. This will make the construction more transparent ?}
\mahmoud{cyclic is the homotopy quotient and negative cyclic the homotopy fixed points}
Note that for two algebras $B$ and $B'$,
\[
\Cyc_*(B) \oplus \Cyc_*(B') \simeq \Cyc_*(B \times B') .
\] 
The corresponding statement for ordinary Hochschild homology is induced by the projections $B \leftarrow B \times B' \to B'$, and any map of algebras that induces a quasi-isomorphism on Hochschild homology induces one on cyclic homology as well.
(See, for instance, \S2.2.12 of \cite{LodayCyclic}.)
Hence, for any finite collection of disjoint opens $U_1$, \dots, $U_k$, 
we have
\[
\cC_A(U_1 \sqcup \cdots \sqcup U_k) \simeq \cC_A(U_1) \oplus \cdots \oplus \cC_A(U_k).
\]
Moreover, for any nested sequence of inclusions $V_1 \subset V_2 \subset \cdots$ with $V = \bigcup_i V_i$,
there is a quasi-isomorphism
\[
{\rm hocolim}(\cC_A(V_1) \to \cC_A(V_2) \to \cdots) \simeq \cC_A(V).
\]
(See E.2.1.1 of \cite{LodayCyclic}.)
In this sense $\cC_A$ behaves like a cosheaf, up to quasi-isomorphism. 
This property underlies the following claim.

@@

\section{A twisted version of LQT}

We step aside from the main body of the paper to describe a natural modification of the prefactorization algebra $\Sym(\cC_A)$. 
Let $\chi \in \Cyc^m(A)$ is a cyclic cocycle of degree $m$. 
Then $\chi$ determines a central extension $\cC(A)_\chi$ of $\Cyc_*(A)[1]$ as an abelian dg Lie algebra (cf. Heisenberg Lie algebras),
but $\chi$ also maps to Lie algebra cochains $\clies(\gl_N(A))$ for every $N$ via the LQT map,
and hence determines a central extension $\gl_N(A)_\chi$ of $\gl_N(A)$ as well.
There is thus a $\chi$-twisted version of the LQT map
\[
\lqt_\chi: \Sym(\cC(A)_\chi) \to \cliels(\gl_N(A)_\chi)
\]
which is a quasi-isomorphism in the large $N$ limit.

This induces $\chi$-twisted versions of all our enveloping $E_n$ algebra theorems (in large $N$ limit) which we can describe using the models prescribed in the main part of the text. 
For simplicity, suppose $A$ is an ordinary (non dg) algebra, and let $\chi \in \Cyc^m(A)$ be a cyclic {\em cocycle} of degree $m$.

\begin{dfn}
Define the precosheaf $\Tilde{\cC}_{A,\chi}$ on $\RR^n$ which assigns to the open $U \subset \RR^n$ the cochain complex
\[
 (U) = \left(\Cyc_*(A \tensor \Omega^*_c(U))[1] \oplus \CC \cdot K , \d_{\rm Cyc} + K \cdot \chi \right) 
\]
where $K$ is a formal parameter of degree $-m+n+1$.
\end{dfn}

Note that when $\chi = 0$, this precosheaf is equivalent to the precosheaf $\cC_A \oplus \ul{\CC}[m-n-1]$, where $\cC_A$ is as in Definition \ref{dfn: CA} and $\ul{\CC}[m-n-1]$ denotes the shifted constant precosheaf.

%Also, $\d_{\rm Cyc}$ is the cyclic differential and $\chi$ is defined on $m$-chains by the pairing between cyclic chains and cochains, together with integration along $U$:
%\[
%\chi ((a_1 \otimes \alpha_1) \tensor \cdots \tensor (a_m \otimes \alpha_m)) = \int_U \<\chi, a_1 \tensor \cdots \tensor a_m\> \alpha_1 \wedge \cdots \wedge \alpha_m.
%\]
%The differential is extended to the entire cochain complex by the graded Leibniz rule. 
%By similar arguments as above, the assignment $U \subset \Tilde{\cC}_{A, \chi}$ is a precosheaf of cochain complexes and $\Sym\left(\Tilde{\cC}_{A,\chi}\right)$ is a prefactorization algebra. 
%As a precosheaf of graded vectors spaces one has $\Tilde{\cC}_{A, \chi} = \cC_A \oplus \ul{\CC}[m-n-1]$, where $\ul{\CC}$ is the constant precosheaf, so that we may think of $\Sym\left(\Tilde{\cC}_{A,\chi}\right)$ as a twisted version of $\Sym(\cC_A)$. 
%These types of twisted \brian{what to say? check my degrees!}
%
